Indirect elicitation as a necessary condition for consistent surrogate losses

### 2020-06-02 neurips-20/cvx-flats.tex
Fixed example in appendix

\section{Omitted examples}
\paragraph{A weather example:}
Consider the following scenario where someone is deciding how to dress for their bike ride.\jessiet{Someone just went to the bike shop...}
They want to wear a rain jacket if it rains, but don't want to have to carry it around if it doesn't rain.
Moreover, they might want their base layer to be appropriate for the heat.
Consider the three outcomes $\Y = \{$sunny, cloudy, rainy$\}$, and we suppose we want to bring a jacket if $Pr[ y= $rain | weather conditions] $ \geq 3/5$.
Moreover, we want to wear a short sleeved shirt if $Pr[y= $sunny | weather conditions] $ \geq$ $Pr[y= $cloudy | weather conditions], and long-sleeved otherwise.

We can now model this problem by a property with the reports $\R = \{$rain jacket and short-sleeve base layer (rj,ss), rain jacket and long-sleeve base layer (rj,ls), no rain jacket, short-sleeve (no rj,ss), no rain jacket, long-sleeve (no rj,ls)$\}$, where $\Gamma(p)$ is shown in Figure~\ref{fig:t-example}.
However, we do not have a target loss for this problem, so constructing a consistent surrogate for this problem is ill-defined without Definition~\ref{def:consistent-prop} unless one takes the time to try to reverse engineer a target loss, which faces the problem of scale as properties become more intricate.

Our bounds from Theorem~\ref{thm:cvx-flats} on the distribution $p = (1/5, 3/5, 1/5)$ suggest that the convex elicitation complexity $\eliccvx(\Gamma) \geq 3 - 0 -1 = 2$, since there is no way to draw a line through $p$ while staying in just one level set on the simplex.
This bound is the same as those given by feasible subspace dimension, but we cannot definitely say anything about convex calibration dimension since we do not have a target loss.
\jessie{Do we want to construct a convex surrogate for this?  Not super clear how...}

This example, although rather silly, can also extend to other decision-tree-like properties that do not have an explicit or easily constructed target loss.

\begin{figure}
	\centering
	\includegraphics[width=0.4\linewidth]{tikz/t-example.pdf}
	\caption{Our example on how to dress for a bike ride.}
	\label{fig:t-example}
\end{figure}

>>>>

\section{Omitted examples}
\paragraph{Discrete problem with no target loss.}
Consider the following scenario where someone is deciding how to dress for the weather based on a meteorologist's forecast.
Consider the three outcomes $\Y = \{$sunny, snowy, rainy$\}$, and we suppose we want to have some bias towards health and safety, so the meteorologist should only predict sunny weather if $Pr[$sunny | weather data$] \geq 3/4$.
Otherwise, they should predict whatever is more likely  given the weather data: rain or snow.

We can now model this problem by a property with the reports $\R = \Y$, and have 
\begin{align*}
\Gamma(p) &= \begin{cases}
\text{sunny} & p_{\text{sunny}} \geq 3/4 \\
\text{rainy} & p_{\text{sunny}} \leq 3/4 \wedge p_{\text{rainy}} \geq p_{\text{snowy}} \\
\text{snowy} & p_{\text{sunny}} \leq 3/4 \wedge p_{\text{snowy}} \geq p_{\text{rainy}} \\
\end{cases}~,~
\end{align*} 
shown in Figure~\ref{fig:t-example}.
Since the cells of elicitable properties in the simplex form a power diagram~\citep{lambert2009eliciting}, we know that there is actually \emph{no} target loss that directly elicits this problem.
Constructing a consistent surrogate for this task is ill-defined without Definition~\ref{def:consistent-prop}.
The function $\propdis(r,p) = \ones\{r \not \in \Gamma(p)\}$, which satisfies the requirements of $\propdis$, now allows us to use Definition~\ref{def:consistent-prop} to think about consistent surrogates for this task.

Our bounds from Theorem~\ref{thm:cvx-flats} on the distribution $p = (1/5, 3/5, 1/5)$ suggest that the convex elicitation complexity $\eliccvx(\Gamma) \geq 3 - 0 -1 = 2$, since there is no way to draw a line through $p$ while staying in just one level set on the simplex.
This bound is the same as those given by feasible subspace dimension, but we cannot apply~\citet[Theorem 16]{ramaswamy2016convex}, which makes a statement about convex calibration dimension, since we do not have a target loss.

This example, although seemingly contrived, can also extend to other decision-tree-like properties that do not have an explicit or easily constructed target loss.

\begin{figure}
	\centering
	\includegraphics[width=0.3\linewidth]{tikz/t-example.pdf}
	\caption{Our meteorology example with a bias towards citizen safety.}
	\label{fig:t-example}
\end{figure}

### 2020-06-02 neurips-20/tikz/t-example.tex
Fixed example in appendix

%t example
\begin{tikzpicture}
\draw[opacity = 0.2] (2,0) -- (-2,0) -- (0,3.46) -- cycle;
%label outcomes
\node at (-2, -0.25) {sunny};
\node at (1/2, 3.5) {rainy};
\node at (2, -0.25) {cloudy};
%level sets

\draw[fill = blue, fill opacity = 0.1, opacity = 0.2] (0, 3.46) -- (-0.8, 2.076) -- (0, 2.076) -- cycle; 
\node at (-0.35, 1.73*1.35) {\footnotesize rj,ss};
\draw[fill = green, fill opacity = 0.1, opacity = 0.2] (0, 3.46) -- (0.8, 2.076) -- (0, 2.076) -- cycle; \node at (0.35, 1.73*1.35) {\footnotesize rj,ls};

\draw[fill = yellow, fill opacity = 0.1, opacity = 0.2] (-2,0) -- (-0.8, 2.076) -- (0, 2.076) -- (0,0) -- cycle; \node at (-0.7, 1) {\footnotesize no rj,ss};
\draw[fill = purple, fill opacity = 0.1, opacity = 0.2] (2,0) -- (0.8, 2.076) -- (0, 2.076) -- (0,0) -- cycle; \node at (0.7, 1.) {\footnotesize no rj,ls};

\node at (0,2.076) {\textbullet};

>>>>

%t example
\begin{tikzpicture}
\draw[opacity = 0.2] (2,0) -- (-2,0) -- (0,3.46) -- cycle;
%label outcomes
\node at (-2, -0.25) {rainy};
\node at (1/2, 3.5) {sunny};
\node at (2, -0.25) {snowy};
%level sets

\draw[fill = blue, fill opacity = 0.1, opacity = 0.2] (0, 3.46) -- (-0.5, 2.595) -- (0.5, 2.595) -- cycle; 
\node at (0, 2.75) {\footnotesize sunny};

\draw[fill = yellow, fill opacity = 0.1, opacity = 0.2] (-2,0) -- (-0.5, 2.595) -- (0, 2.595) -- (0,0) -- cycle; \node at (-0.7, 1) {\footnotesize rainy};
\draw[fill = green, fill opacity = 0.1, opacity = 0.2] (2,0) -- (0.5, 2.595) -- (0, 2.595) -- (0,0) -- cycle; \node at (0.7, 1.) {\footnotesize snowy};

\node at (0,2.595) {\textbullet};
